---
title: "The Replication Observatory"
subtitle: "A Living Report on Journal Practices"
author: "Powered by the FLoRA Dataset"
date: today
date-format: long
execute:
  echo: false
  warning: false
  message: false
---

::: {.intro-box}
**Welcome to the Replication Observatory.** 

Science is a cumulative endeavor. To understand the robustness of our literature, we must track not only *what* is replicated, but *where* these conversations happen. This living report dynamically connects to the [FLoRA database](https://forrt.org/) to provide an up-to-date overview of replication outcomes across academic journals. 

Toggle **Dark / Light Mode** in the top right, use the **search boxes** to find specific journals, or **click and drag** the plots vertically to scroll through the data.
:::

```{r setup-and-data}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(plotly)
library(crosstalk)
library(DT)
library(forcats)

# 1. Fetch Live Data
# The document pulls this fresh every time it compiles
url <- "https://raw.githubusercontent.com/forrtproject/FReD-data/refs/heads/main/output/flora.csv"
df <- read.csv(url, stringsAsFactors = FALSE, na.strings = c("", "NA"))

# 2. Clean and Standardize Data
df_clean <- df %>% 
  filter(tolower(type) == "replication") %>% 
  mutate(outcome = tools::toTitleCase(tolower(trimws(outcome)))) %>% 
  mutate(outcome = case_when(
    outcome == "Successful" ~ "Successful",
    outcome == "Failed" ~ "Failed",
    outcome == "Mixed" ~ "Mixed",
    outcome == "Uninformative" ~ "Uninformative",
    outcome == "Descriptive Only" ~ "Descriptive Only",
    outcome == "Statistically Successful But Flawed" ~ "Stat. Successful but Flawed",
    TRUE ~ "Other"
  ))

# 3. Define Warm, Professional Institutional Palette
color_map <- c(
  "Successful" = "#4CAF50", # Warm Green
  "Mixed"      = "#FFB300", # Warm Amber
  "Failed"     = "#E53935", # Softened Red
  "Uninformative" = "#9E9E9E", # Neutral Grey
  "Descriptive Only" = "#BDBDBD", # Light Grey
  "Stat. Successful but Flawed" = "#757575", # Dark Grey
  "Other"      = "#E0E0E0"  # Very Light Grey
)

# 4. Developer Helper: Function to build standardized crosstalk/plotly pairs
build_journal_plot <- function(df_input, journal_col, title_x) {
  
  # Summarize data
  summary_df <- df_input %>%
    filter(!is.na(!!sym(journal_col))) %>%
    count(!!sym(journal_col), outcome) %>%
    pivot_wider(names_from = outcome, values_from = n, values_fill = list(n = 0)) %>%
    mutate(Total = rowSums(across(where(is.numeric)))) %>%
    mutate(Successful = if("Successful" %in% names(.)) Successful else 0) %>%
    # Order by Total descending, then Successful
    arrange(desc(Total), desc(Successful)) %>%
    # Lock in factor levels for Plotly
    mutate(!!sym(journal_col) := factor(!!sym(journal_col), levels = unique(!!sym(journal_col))))
  
  # Initialize Crosstalk shared data
  shared_data <- SharedData$new(summary_df)
  
  # Build Plotly
  p <- plot_ly(shared_data, y = as.formula(paste0("~`", journal_col, "`")), height = 600)
  
  # Add stacked bars dynamically based on available categories
  for(out in names(color_map)) {
    if(out %in% names(summary_df)) {
      p <- p %>% add_bars(
        x = as.formula(paste0("~`", out, "`")), 
        name = out, 
        marker = list(color = color_map[[out]])
      )
    }
  }
  
  # Apply layout: Stacked, Top 10 view by default, responsive to dark/light mode
  p <- p %>% layout(
    barmode = 'stack',
    plot_bgcolor = "rgba(0,0,0,0)",
    paper_bgcolor = "rgba(0,0,0,0)",
    font = list(color = "var(--bs-body-color)"),
    hovermode = "y unified",
    margin = list(l = 250), # Give room for long journal names
    xaxis = list(
      title = title_x, 
      gridcolor = "var(--bs-border-color)"
    ),
    yaxis = list(
      title = "",
      autorange = "reversed", # Highest total at the top
      range = c(-0.5, 9.5),   # SHOW ONLY TOP 10 BY DEFAULT
      fixedrange = FALSE      # Allow zooming/panning
    )
  )
  
  return(list(shared = shared_data, plot = p, col = journal_col))
}
```

## Publishers of Replications

Which journals are driving the open science movement by actively publishing replication attempts? The chart below highlights the top publishers. 

*💡 **Tip:** The chart displays the **Top 10** journals by default. **Click and drag vertically** inside the chart to scroll down and view more journals, or use the search box to find a specific journal.*

```{r publishers-plot}
plot_data_r <- build_journal_plot(df_clean, "journal_r", "Number of Published Replications")

# UI Layout for Search + Plot
bscols(
  widths = c(12, 12),
  filter_select("search_r", "Search for a Publishing Journal:", plot_data_r$shared, ~journal_r, multiple = FALSE),
  plot_data_r$plot
)
```

<hr style="margin: 40px 0;">

## Targets of Replications

Conversely, which journals originally published the studies that are being replicated? A high number here indicates high impact and scrutiny, a natural part of the scientific lifecycle. 

```{r targets-plot}
plot_data_o <- build_journal_plot(df_clean, "journal_o", "Number of Targeted Original Studies")

# UI Layout for Search + Plot
bscols(
  widths = c(12, 12),
  filter_select("search_o", "Search for a Targeted Journal:", plot_data_o$shared, ~journal_o, multiple = FALSE),
  plot_data_o$plot
)
```

<hr style="margin: 40px 0;">

## Comprehensive Data Table

For a detailed, sortable view of all original targeted journals and their specific replication outcomes, please consult the table below. You can download or filter the data directly from your browser.

```{r datatable}
# Prepare the data for the table 
table_data <- df_clean %>%
  filter(!is.na(journal_o)) %>%
  count(journal_o, outcome) %>%
  pivot_wider(names_from = outcome, values_from = n, values_fill = list(n = 0)) %>%
  mutate(Total = rowSums(across(where(is.numeric)))) %>%
  relocate(journal_o, Total) %>%
  arrange(desc(Total)) %>%
  rename(`Original Journal` = journal_o)

# Create the interactive DataTable
datatable(
  table_data,
  rownames = FALSE,
  extensions = 'Buttons',
  options = list(
    pageLength = 10,
    autoWidth = TRUE,
    order = list(list(1, 'desc')), 
    dom = '<"top"fB>rt<"bottom"lip><"clear">',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = 'cell-border stripe hover' 
)
```